Single-cell virus sequencing of influenza infections that trigger innate immunity

### 2018-10-04 paper/paper.tex
minor edits

%%% begin mutations figure %%%
\begin{figure}
\begin{fullwidth}
{\centering
\includegraphics[width=\linewidth]{figures/single_cell_figures/p_mutations.pdf}
}
\caption{
Viral features associated with heterogeneity in infection outcome among cells for which we sequenced all expressed viral genes.
{\bf (A)} 
Percent of all mRNA derived from virus, faceted by whether cells express unmutated copies of all eight genes.
Cells infected by full wild-type virus exhibit less heterogeneity in viral burden as quantified by the Gini index (95\% confidence intervals are indicated).
{\bf (B)}
Cells infected by full wild-type virus to express less IFN.
{\bf (C)}
Specific viral defects associated with IFN induction.
The top panel show the percent of IFN- and IFN+ cells that fail to express each viral gene.
The middle and bottom panels show the percent of IFN- and IFN+ cells that have a deletion or amino-acid substitution in each gene, conditioned on the cell expressing that gene.
Numbers give P-values (Fisher's exact test) and associated Q-values~\citep{storey2003statistical} for rejecting the null hypothesis that percents are equal among IFN- and IFN+ cells. 
\FIGSUPP[mutations]{allcells} shows the trends are similar if we include infected cells with incomplete viral sequence information. 
\FIGSUPP[mutations]{isg} shows the trends are similar if we categorize cells by ISG expression rather than IFN expression.
{\bf (D)}
There is no association between IFN induction and the amount of viral mRNA in cells that express NS, but viral burden is associated with IFN induction among cells that lack NS.
Throughout this figure, we only consider substitutions that are non-synonymous.
Insertions are not shown as a mutation type as they are extremely rare (\FIG{genotypes}).
}
\label{fig:mutations}

@@

Viral defects also associated with IFN induction, with cells infected by full wild-type virions turning IFN+ less often than cells infected by incomplete or mutated virions (\FIG{mutations}B).
Specific viral defects were especially associated with IFN induction (\FIG{mutations}C).
Absence of NS and amino-acid mutations in PB1 were significantly enriched in IFN+ cells, and amino-acid mutations in NS and deletions in HA were weakly enriched.
Only the absence of NS remained significant at a false discovery rate of 10\% (\FIG{mutations}C)---although a Bayesian-minded virologist might contend that controlling for all the hypotheses in \FIG{mutations}C is too stringent, since some are more plausible \textit{a priori} given existing biological knowledge~\citep[e.g.,][]{killip2017single, velthuis2018mini, wu2014high}.
In any case, \FIG{genotypes} and \FIG{mutations}C motivate compelling hypotheses about specific viral defects that contribute to IFN induction, and below we pursue these hypotheses using experimental follow-up.

@@

We tested the rate of IFN induction by each viral stock using the reporter cells.
\FIG{validation} shows that five of the eight mutant viral stocks induced IFN more frequently than wild type.
The strongest IFN induction was by the NS1stop virus, but the PB1 internal deletion and three of the point-mutant viruses (PB1-D27N, PB1-T677A, and NS1-A122V) also induced significantly more IFN than wild-type.
These results show that the viral defects in single IFN+ cells often cause increased IFN production.

>>>>

%%% begin mutations figure %%%
\begin{figure}
\begin{fullwidth}
{\centering
\includegraphics[width=\linewidth]{figures/single_cell_figures/p_mutations.pdf}
}
\caption{
Viral features associated with heterogeneity in infection outcome among cells for which we sequenced all expressed viral genes.
{\bf (A)} 
Percent of all mRNA derived from virus, faceted by whether cells express unmutated copies of all eight genes.
Cells infected by fully wild-type virus exhibit less heterogeneity in viral burden as quantified by the Gini index (95\% confidence intervals are indicated).
{\bf (B)}
Cells infected by fully wild-type virus to express IFN less frequently.
{\bf (C)}
Specific viral defects associated with IFN induction.
The top panel show the percent of IFN- and IFN+ cells that fail to express each viral gene.
The middle and bottom panels show the percent of IFN- and IFN+ cells that have a deletion or amino-acid substitution in each gene, conditioned on the cell expressing that gene.
Numbers give P-values (Fisher's exact test) and associated Q-values~\citep{storey2003statistical} for rejecting the null hypothesis that percents are equal among IFN- and IFN+ cells. 
\FIGSUPP[mutations]{allcells} shows the trends are similar if we include infected cells with incomplete viral sequence information. 
\FIGSUPP[mutations]{isg} shows the trends are similar if we categorize cells by ISG expression rather than IFN expression.
{\bf (D)}
There is no association between IFN induction and the amount of viral mRNA in cells that express NS, but viral burden is associated with IFN induction among cells that lack NS.
Throughout this figure, we only consider substitutions that are non-synonymous.
Insertions are not shown as a mutation type as they are extremely rare (\FIG{genotypes}).
}
\label{fig:mutations}

@@

Viral defects are also associated with IFN induction, with cells infected by full wild-type virions expressing IFN less often than cells infected by incomplete or mutated virions (\FIG{mutations}B).
Specific viral defects were especially associated with IFN induction (\FIG{mutations}C).
Absence of NS and amino-acid mutations in PB1 were significantly enriched in IFN+ cells, and amino-acid mutations in NS and deletions in HA were weakly enriched.
Only the absence of NS remained significant at a false discovery rate of 10\% (\FIG{mutations}C)---although a Bayesian-minded virologist might contend that controlling for all the hypotheses in \FIG{mutations}C is too stringent, since some are more plausible \textit{a priori} given existing biological knowledge~\citep[e.g.,][]{killip2017single, velthuis2018mini, wu2014high}.
In any case, \FIG{genotypes} and \FIG{mutations}C motivate compelling hypotheses about specific viral defects that contribute to IFN induction, and below we pursue these hypotheses using experimental follow-up.

@@

We tested the rate of IFN induction by each viral stock using the reporter cells.
\FIG{validation} shows that five of the eight mutant viral stocks induced IFN more frequently than wild type.
The strongest IFN induction was by the NS1stop virus, but the PB1 internal deletion and three of the point-mutant viruses (PB1-D27N, PB1-T677A, and NS1-A122V) also induced IFN significantly more frequently than wild-type.
These results show that the viral defects in single IFN+ cells often cause increased IFN production.
